Turbulence in compact to giant HII regions

### 2021-09-10 mnras_template.tex
Fix fig names to remove spaces
Javier changes 1021-09-10

\section{Introduction}

It is known that the speed of sound in a HII region is of the order of \(c_{HII} \sim\) 13 km s\kms.
\citet{smith1970} discovered that the probable velocities of internal motions of extragalactic HII regions, \(\sigma_{W}\) (line width integrated over the whole HII region), were in the range of $\sim$ 19-34 km s\kms\ covering supersonic values.
\citet{skillman1984kinematics} found broad profiles in giant extragalactic HII regions (GEHRs) that have a FWHM\(>\)30km s\kms. 
This property is mainly used to distinguish between 'normal' and 'giant' HII regions. Other differences are their size, luminosity and their stellar population. 
For the velocity to be supersonic it is necessary a continuous mechanism to maintain the observed motions, as supersonic motions are expected to dissipate energy via shocks \citep{1994Ap&SS.216..285C}.
Also, this non-thermal broadening on the spectral emission lines has been suggested as evidence of disorder motions along the line-of-sight (LOS) of the ionized gas. 
Turbulence is suggested as a mechanism that can stir the medium and maintain the supersonic velocities. 
The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ - 10$^{9}$, are the main properties that supports the idea of a turbulent interstellar medium.
Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} revealed that different phases of the interstellar medium show fluctuations on their velocity field that can be interpreted as evidence of random motions.
The usual picture considers that interstellar turbulence is driven on different scales by various energetic processes.
Also, it is thought that the formation of structures like filaments and shells in the diffuse medium is determined by large-scale turbulence.
Stars are the mainly mechanism proposed to account for the large input of kinetic energy through UV radiation, but the dominant energetic sources and their relation to turbulence still is unclear.

@@

\begin{figure*}
\centering
\begin{multicols}{3}
\includegraphics[width=1.5in]{Figures/Hist/604}\par
\includegraphics[width=1.5in]{Figures/Hist/595}\par
\includegraphics[width=1.5in]{Figures/Hist/346}\par
\end{multicols}
\begin{multicols}{3}
\includegraphics[width=1.5in]{Figures/Hist/Hubble V}\par
\includegraphics[width=1.5in]{Figures/Hist/Hubble X}\par
\includegraphics[width=1.5in]{Figures/Hist/30Dor}\par
\end{multicols}
\begin{multicols}{3}
\includegraphics[width=1.5in]{Figures/Hist/M8}\par
\includegraphics[width=1.5in]{Figures/Hist/Car}\par
\includegraphics[width=1.5in]{Figures/Hist/OrionS}\par
\end{multicols}
\caption{Histograms of the centroid velocities of our sample of HII regions. }
\label{fig:hist}
\end{figure*}

@@

@@

\begin{table*}
\begin{center}\caption{Parameters of the linear regression (Y = aX + b).}
\begin{tabular}{cccccc}\hline
Y                    &X         &a               &b                &r     & p                \\ \hline
log \(r_0\)          &log \(R\) &0.65\(\pm\)0.06 &-0.83\(\pm\)0.11 & 0.96 & <10\(^{-5}\)    \\ 
log \(\sigma\)       &log \(L\) &0.16\(\pm\)0.05 &-5.54\(\pm\)2.13 & 0.71 & 0.02             \\
log \(m\)            &log \(D\) &0.05\(\pm\)0.02 &-0.05\(\pm\)0.03 & 0.73 & 0.02  \\ 
*log \(\sigma_{LOS}\) &log \(L\) &0.145\(\pm\)0.008 &-4.42\(\pm\)0.33 & 0.77 & <10\(^{-5}\)  \\ 
*log \(L\) &log \(\sigma_{LOS}\) &4.09\(\pm\)0.23 &34.17\(\pm\)0.32 & 0.77 & <10\(^{-5}\)  \\ 
log \(\sigma\)       &log \(\sigma_{LOS}\) &0.77\(\pm\)0.28 &-0.21\(\pm\)0.32 &0.72 & 0.02 \\ \hline
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

@@

\begin{figure}
\centering 
\includegraphics[width=2in]{Figures/sigmas.pdf}
\caption{}
\label{fig:sigvssig}
\end{figure}

>>>>

\section{Introduction}
\WILL{I think it would be best to lead with a description of the dynamics of H II regions before mentioning the turbulence}.

It is known that the speed of sound in a HII region is of the order of \(c_{HII} \sim\) 13 km s\kms.
\citet{smith1970} discovered that the probable velocities of internal motions of extragalactic HII regions, \(\sigma_{W}\) (line width integrated over the whole HII region), were in the range of $\sim$ 19-34 km s\kms\ covering supersonic values.
\citet{skillman1984kinematics} found broad profiles in giant extragalactic HII regions (GEHRs) that have a FWHM\(>\)30km s\kms. 
This property is mainly used to distinguish between 'normal' and 'giant' HII regions. Other differences are their size, luminosity and their stellar population. 
For the velocity to be supersonic it is necessary a continuous mechanism to maintain the observed motions, as supersonic motions are expected to dissipate energy via shocks \citep{1994Ap&SS.216..285C}.
Also, this non-thermal broadening on the spectral emission lines has been suggested as evidence of disorder motions along the line-of-sight (LOS) of the ionized gas. 
Turbulence is suggested as a mechanism that can stir the medium and maintain the supersonic velocities. 
The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ - 10$^{9}$, are the main properties that supports the idea of a turbulent interstellar medium.
Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} revealed that different phases of the interstellar medium show fluctuations on their velocity field that can be interpreted as evidence of random motions.

The usual picture considers that interstellar turbulence is driven on different scales by various energetic processes.
Also, it is thought that the formation of structures like filaments and shells in the diffuse medium is determined by large-scale turbulence.
Stars are the mainly mechanism proposed to account for the large input of kinetic energy through UV radiation, but the dominant energetic sources and their relation to turbulence still is unclear.

@@

\begin{figure*}
\centering
\begin{multicols}{3}
\includegraphics[width=1.5in]{Figures/Hist/604}\par
\includegraphics[width=1.5in]{Figures/Hist/595}\par
\includegraphics[width=1.5in]{Figures/Hist/346}\par
\end{multicols}
\begin{multicols}{3}
\includegraphics[width=1.5in]{Figures/Hist/Hubble-V}\par
\includegraphics[width=1.5in]{Figures/Hist/Hubble-X}\par
\includegraphics[width=1.5in]{Figures/Hist/30Dor}\par
\end{multicols}
\begin{multicols}{3}
\includegraphics[width=1.5in]{Figures/Hist/M8}\par
\includegraphics[width=1.5in]{Figures/Hist/Car}\par
\includegraphics[width=1.5in]{Figures/Hist/OrionS}\par
\end{multicols}
\caption{Histograms of the centroid velocities of our sample of HII regions. }
\label{fig:hist}
\end{figure*}

@@

\subsection{Correlations between turbulent parameters}

\begin{figure}
\centering 
\includegraphics[width=2in]{Figures/mr0.pdf}
\caption{ }
\label{fig:mr0}
\end{figure}

@@

\begin{table*}
\begin{center}\caption{Parameters of the linear regression (Y = aX + b).}
\begin{tabular}{cccccc}\hline
Y                    &X         &a               &b                &r     & p                \\ \hline
log \(r_0\)          &log \(R\) &0.65\(\pm\)0.06 &-0.83\(\pm\)0.11 & 0.96 & <10\(^{-5}\)    \\ 
log \(\sigma\)       &log \(L\) &0.16\(\pm\)0.05 &-5.54\(\pm\)2.13 & 0.71 & 0.02             \\
log \(m\)            &log \(D\) &0.05\(\pm\)0.02 &-0.05\(\pm\)0.03 & 0.73 & 0.02  \\ 
*log \(\sigma_{LOS}\) &log \(L\) &0.145\(\pm\)0.008 &-4.42\(\pm\)0.33 & 0.77 & <10\(^{-5}\)  \\ 
*log \(L\) &log \(\sigma_{LOS}\) &4.09\(\pm\)0.23 &34.17\(\pm\)0.32 & 0.77 & <10\(^{-5}\)  \\ 
log \(\sigma\)       &log \(\sigma_{LOS}\) &0.72\(\pm\)0.27 &-0.14\(\pm\)0.31 &0.68 & 0.02 \\ \hline
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

@@

\begin{figure}
\centering 
\includegraphics[width=2in]{Figures/sigmas.pdf}
\caption{Log \(\sigma_{LOS}\) vs Log \(\sigma\) plot. The values are taken from Table \ref{tab:Res}. The solid-gray line indicate perfect correlation and the dotted-black line indicate the relation in Table \ref{tab:RestStats}. The size of the markers indicate the distance to the region, the bigger the marker the farther the region. }
\label{fig:sigvssig}
\end{figure}
